Results

### 2018-05-07 4-results-simus.Rmd
final figures

methods.color <- setNames(c(scales::hue_pal()(6), "black"), 
                          c("logit-simple", "PRS-max", "PRS-stringent",
                            "T-Trees", "logit-triple", "PRS-all", "biglasso")) 
```

>>>>

methods.color <- setNames(
  c(scales::hue_pal()(6), c("black", "blue", "green")), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all", 
    "biglasso", "logit-simple-enet-ridge", "logit-simple-lasso")
) 
```
